BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-10 tex/3-algorithms.tex
Minor corrections and comments in chapter 3

This section explains in detail the algorithm we developed to extract blog posts article and its variations for authors, dates and comments. Our approach uses blog specific characteristics to build extraction rules applicable to all posts of a blog\comment{"all posts of a blog" needs a better formulation.}. Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.

@@

% html extraction is not trival
Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}. For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page \cite{w3c2002}. More recently, specifications such as microdata \cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2013}. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise structure of pages \cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008-a}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.

@@

% observations when working with blogs
Having blogs as our target websites, we use the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog,
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 blog posts, often less than the total number of posts in blogs \cite{oita2010}. Consequently, in order to effectively archive old content from blogs, it is necessary to download and process pages beyond the ones referenced in web feeds.

@@

% per blog procedure, related work
To extract content from blog posts, we proceed by building extraction rules from the data given in the blog's web feed. The idea is to use a set of \emph{training data}, pairs of HTML page and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.

% input from observations.
Observation \ref{havefeedAssum} allows the crawler to obtain inputs for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as target content such as the article, its title, authors and publication date. Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

@@

% abs, plan
Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section. \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction. In \ref{timecomplexityandlinearreformulation} we analyse time complexity of \autoref{extractionAlgo} and give a linear time reformulation using dynamic programing. Finally, \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

@@

% xpath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, thus providing the \code{Apply} function, used in \autoref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection with the absolute path in the HTML tree. \code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better consistency than absolute paths over pages of a blog. For these reasons, the \coderef{allrulesAlgo} function returns a single rule per node:

@@

% score function := string similarity
Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process. When targeting articles, extraction rules are scored with a string similarity function comparing the extracted and the target strings. We chose the Sørensen–Dice coefficient similarity \cite{dice1945}, which is, to the best of our knowledge, the only string similarity algorithm fulfilling the following criteria:

@@

Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article. \autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.

@@

% into: algo 1 defined
The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is completed. We now proceed with a time complexity analysis.

% algo 1 is quadratic
First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}. As stated before, the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument. Therefore, the body of the inner loop will be executed \Oof{n} times. Because each extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.

@@

% intro
Using string similarity as the only score measurement leads to poor performances on author and date extractions, and is not suitable for comment extraction. This subsection presents variations of the previously presented \code{ScoreFunction} which addresses issues of these other contents.

% authors
The case of authors is problematic because authors' names often appear in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score. The heuristic we use to get around this issue consists in adding a new component in the \code{ScoreFunction} for author extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new component takes advantage of the positioning of post's authors which often is a direct child or shares its parent with the post content node.

% dates
Dates are affected by the same duplication issue, as well as the inconsistency of format between web feeds and web pages. Our solution for date extraction extends the \code{ScoreFunction} for authors by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original date obtained from the web feed. For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on. So far we do not support dates in multiple languages, but adding new target formats base and languages detection would be a simple extension of our date extraction algorithm.

% comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from the post web page. To do so we use the following \code{ScoreFunction}:
\begin{itemize}
  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with overflow on its comment feed, thus supporting blogs with multiple commenting engines. Comment contents are extracted first, which allows us to narrow down the initial filtering by fixing a target number of comments.

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of each nodes of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity. Scoring rules for comment extraction requires a more expensive algorithm. However, this is compensated by the fact that the proportion of candidates left, after filter out rules not returning enough results, is very low in practice. Analog reformulations to the one done with \autoref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}.

>>>>

This section explains in detail the algorithm we developed to extract blog posts articles \comment{should we explain here that article is the actual content (text) of a blog post? Or is it already clear enough?} as well as its variations for authors, dates and comments. Our approach uses blog specific characteristics to build extraction rules applicable to all posts of a blog\comment{"all posts of a blog" needs a better formulation.}. Our focus is on minimizing the algorithmic complexity while keeping our approach simple and generic.

@@

% html extraction is not trival
Extracting metadata and content from HTML documents is a challenging task. Standards and format recommendations have been around for quite some time, strictly specifying how HTML documents should be organised \cite{w3c2013}. For instance the \code{<h1></h1>} tags have to contain the highest-level heading of the page and must not appear more than once per page \cite{w3c2002}. More recently, specifications such as microdata \cite{whatwg2013} define ways to embed semantic information and metadata inside HTML documents, but these still suffer from very low usage: estimated to be used in less than 0.5\% of websites \cite{andrewrogers2013}. In fact, the majority of websites rely on the generic \code{<span></span>} and \code{<div></div>} container elements with custom \code{id} or \code{class} attributes to organise the structure of pages \cite{brianwilson2008}, and more than 95\% of pages do not pass HTML validation \cite{brianwilson2008-a}. Under such circumstances, relying on HTML structure to extract content from web pages is not viable and other techniques need to be employed.

@@

% observations when working with blogs
Having blogs as our target websites, we made the following observations which play a central role in the extraction process\Anote{observations}:
\begin{enumerate}[label={(\arabic*)}]
  \item\label{havefeedAssum} Blogs provide web feeds: structured and standardized views of the latest posts of a blog,
  \item\label{similarhtmlAssum} Posts of the same blog share a similar HTML structure.
\end{enumerate}
Web feeds usually contain about 20 blog posts, often less than the total number of posts in blogs \cite{oita2010}\comment{is this reference for the fact that feeds usually contain about 20 blog posts or for the fact that this number is often smaller than the total number of posts in a blog?}. Consequently, in order to effectively archive the entire content of a blog, it is necessary to download and process pages beyond the ones referenced in web feed.

@@

% per blog procedure, related work
To extract content from blog posts, we proceed by building extraction rules from the data given in the blog's web feed. The idea is to use a set of \emph{training data}, pairs of HTML pages and target content, which are used to build an extraction rule capable of locating the target content on each HTML page.

% input from observations.
Observation \ref{havefeedAssum} allows the crawler to obtain input for the extraction rule builder algorithm: each web feed entry contains a link to the corresponding web page as well as target content such as the article, its title, authors and publication date. Observation \ref{similarhtmlAssum} guarantees the existence of an appropriate extraction rule, as well as its applicability to all posts of the blog.

@@

% abs, plan
Functions in \autoref{extractionAlgo} are voluntarily abstract at this point and will be explained in detail in the remaining of this section. Section \ref{extractionrulesandstringsimilarity} defines \code{AllRules}, \code{Apply} and the \code{ScoreFunction} we use for article extraction. In section \ref{timecomplexityandlinearreformulation} we analyse the time complexity of \autoref{extractionAlgo} and give it a linear time reformulation using dynamic programing. Finally, section \ref{variationsforauthorsdatesandcomments} shows how the \code{ScoreFunction} can be adapted to extract authors, dates and comments.

@@

% xpath selectors (id, else class, else path)
In our implementation, rules are queries in the XML Path Language (XPath). Consequently, standard libraries can be used to parse HTML pages and apply extraction rules, providing the \code{Apply} function used in \autoref{extractionAlgo}. We experimented with 3 types of XPath queries: selection over the HTML \code{id} attribute, selection over the HTML \code{class} attribute and selection using the absolute path in the HTML tree. \code{id} attributes are expected to be unique, and \code{class} attributes have showed to have better consistency than absolute paths over pages of a blog\comment{this is an observation right? Maybe add something like have showd in our experiments...}. For these reasons\comment{there is a misscontinuation here. It's not for these reasons that we return a single rule per node. It's because we only need one rule per node. The rule is expressed in one of the three types mentioned above.}, the \coderef{allrulesAlgo} function returns a single rule per node:

@@

% score function := string similarity
Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process. When targeting articles, extraction rules are scored\comment{scored has a different meaning here. Graded or sorted or something similar is more correct} with a string similarity function comparing the extracted strings with the target strings. We chose the Sørensen–Dice coefficient similarity \cite{dice1945}, which is, to the best of our knowledge, the only string similarity algorithm fulfilling the following criteria:

@@

Properties \ref{wordorderProp} and \ref{lengthProp} are essential when we deal with cases where the blog's web feed only contains an abstract or a subset of the entire post article. \autoref{similarityTable} gives examples to illustrate how these two properties hold for the Sørensen–Dice coefficient similarity but do not for \emph{edit distance} based similarities such as the Levenshtein \cite{levenshtein1966} similarity.

@@

% into: algo 1 defined
The functions \coderef{allrulesAlgo}, \code{Apply} and \coderef{similarityAlgo} (as \code{ScoreFunction}) being defined, the definition of \autoref{extractionAlgo} for article extraction is complet. We now proceed with a time complexity analysis.

% algo 1 is quadratic
First, let's assume that we have at our disposal a linear time HTML parser that constructs an appropriate data structure, indexing HTML nodes on their \code{id} and \code{class} attributes, effectively making \code{Apply}~$\in$~\Oof{1}. As stated before, the outer loop splits the input into independent computations and each call to \coderef{allrulesAlgo} returns (in linear time) at most as many rules as the number of nodes in its \emph{page} argument. Therefore, the body of the inner loop will be executed \Oof{n} times. Because each extraction rule can return any subtree of the queried page, each call to \coderef{similarityAlgo} takes \Oof{n}, leading to an overall quadratic running time.

@@

% intro
Using string similarity as the only score measurement leads to poor performance on author and date extraction, and is not suitable for comment extraction. This subsection presents variations of the previously presented \code{ScoreFunction} which addresses issues of these other types of content.

% authors
The case of authors is problematic because authors' names often appear in multiple places of a page, which results in several rules with maximum \coderef{similarityAlgo} score. The heuristic we use to get around this issue consists of adding a new component in the \code{ScoreFunction} for author extraction rules: the \emph{tree distance} between the evaluated node and the post content node. This new component takes advantage of the positioning of a post's authors node which often is a direct child or shares its parent with the post content node.

% dates
Dates are affected by the same duplication issue, as well as the inconsistency of format between web feeds and web pages. Our solution for date extraction extends the \code{ScoreFunction} for authors by comparing the \emph{extracted} string to multiple \emph{targets}, each being a different string representation of the original date obtained from the web feed. For instance, if the feed indicates that a post was published on \stringliteral{Thu, 01 Jan 1970 00:00:00}, our algorithm will search for a rule that returns one of \stringliteral{Thursday January 1, 1970}, \stringliteral{1970-01-01}, \stringliteral{43 years ago} and so on. So far we do not support dates in multiple languages, but adding new target formats base\comment{is the word base needed here?} and languages detection would be a simple extension of our date extraction algorithm.

% comments
Comments are usually available in separate web feeds, one per blog post. Similarly to blog feeds, comment feeds have a limited number of entries, and when the number of comments on a blog post exceeds this limit, comments have to be extracted from the post web page. To do so we use the following \code{ScoreFunction}:
\begin{itemize}
  \item Rules returning less HTML nodes than the number of comments on the feed are filtered out with a zero score,
  \item Remaining rules are scored with the value of the \emph{maximum weighted matching} in the \emph{complete bipartite graph} $G = (U, V, E)$, where $U$ is the set of HTML nodes returned by the rule, $V$ is the set of target comment fields from the web feed (such as comment authors) and $E(u, v)$ as\comment{did you mean 'is a' instead of 'as'?} weight equal to \coderef{similarityAlgo}\code{(}\emph{u, v}\code{)}.
\end{itemize}
Our crawler executes this algorithm on each post with an overflow on its comment feed, thus supporting blogs with multiple commenting engines. The comment content is extracted first, allowing us to narrow down the initial filtering by fixing a target number of comments.

% rush some time complexity analysis
Regarding time complexity, computing the \emph{tree distance} of each node of a graph to a single reference node can be done in linear time, and multiplying the number of targets by a constant factor does not affect the asymptotic computational complexity. Scoring\comment{like before, Scoring should be Grading or Sorting or something like that} rules for comment extraction requires a more expensive algorithm. However, this is compensated by the fact that the proportion of candidates left, after filtering out rules not returning enough results, is very low in practice. Similar reformulations to the one done with \autoref{linearAlgo} can be applied on each \code{ScoreFunction} in order to minimize the time spent in \coderef{similarityAlgo}. \comment{This last sentence might make the reader think: if they can be applied, they why didn't you apply them?}

### 2013-12-10 tex/4-techniques.tex
Minor corrections and comments in chapter 3

This section gives an overview of different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture will then be discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage. Finally we will talk about the design choices we made in view of large scale deployment.

>>>>

This section gives an overview of the different techniques used in our crawler. We first show how we integrated a headless web browser into the harvesting process to support blogs that use JavaScript to display page content. The overall software architecture is then discussed, introducing the Scrapy framework and the enrichments we implemented for our specific usage. Finally we talk about the design choices we made in view of a large scale deployment.
